\begin{abstract}
Prediction markets aggregate collective intelligence into probability estimates, yet individual participants consistently struggle to outperform market consensus. We present Murmur, a system that automatically discovers effective prediction strategies through three complementary mechanisms. First, a \emph{Context Planner} identifies domain-specific knowledge gaps for each prediction event and injects real-time context---commodity prices, breaking news, precursor signals, and structured decompositions---before querying a large language model. Second, an \emph{Evolution Engine} treats the prediction strategy itself as mutable source code, iteratively rewriting analysis logic against resolved market outcomes rather than merely tuning numerical parameters. Third, a \emph{Virtual Prediction Market} populates a simulated exchange with heterogeneous trading agents to stress-test candidate strategies under adversarial conditions. We validate Murmur on Polymarket, the largest decentralized prediction market, across a corpus of over 1{,}000 resolved events spanning 11 domains. Context-enriched predictions demonstrate 8--11\% accuracy improvement in information-sensitive domains such as entertainment awards and commodity pricing, where structured context injection closes the gap between LLM reasoning capability and real-time market knowledge. Our evolutionary code search discovers strategies that match market-level Brier Scores (0.0934 vs.\ 0.0936 market baseline) while providing interpretable, auditable prediction rationales. We further analyze the domain-dependent nature of prediction alpha, finding that exploitable inefficiencies concentrate in low-liquidity markets with asymmetric information flow, while high-volume markets such as sports betting remain efficiently priced. Murmur's architecture generalizes beyond prediction markets: the same engine powers supply chain simulation and healthcare coordination in companion systems, demonstrating that context-aware agent-based reasoning constitutes a transferable framework for decision-making under uncertainty.
\end{abstract}
